Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-06-30 Final_Manuscript.Rmd
reorganized files

```{r data}
clark_measures <- read.csv("Cleaned data/clark_measures.csv")
smith <- read.csv("Cleaned data/smith.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
```

>>>>

```{r data}
clark_measures <- read.csv("Cleaned data/clark_measures.csv")
smith <- read.csv("Cleaned data/smith.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")

smith$inter_1
```

### 2020-06-30 Final_Manuscript.tex
reorganized files

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Kat Kyuchukova, Asha Hinson, \& Randi L. Garcia},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Objectification in Action: Self- and Other-Objectification in
Same-gender Interactions}
    \author{Kat Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \&
Randi L. Garcia\textsuperscript{1}}
    \date{}

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\

\abstract{
Objectification theory is a valuable framework for conceptualizing the
psychological consequences of being female within a society that
sexually objectifies the female body, and considering the ways in which
girls and women are acculturated to then internalize an observer's
perspective as a primary view of their appearance. Empirical evidence
has largely elucidated links between objectification,
self-objectification, and negative outcomes for woman within
interpersonal interactions between male-female pairs particularly. The
purpose of the present study was to extend past research and consider
the relationships between such valuable phenomena and their effects on
authenticity within interactions between female pairs. Woman were
brought into the laboratory and interacted in same-sex dyads. Dyadic
analysis was utilized to detect whether partners' objectification of
each other affected state self-objectification, and the resulting
feelings of comfort and authenticity during the interaction. After the
interaction, participants completed a questionnaire which measured many
constructs including cognitive performance, career aspirations, and
relationship agency. Results revealed no significant relationship
between self-objectification and authenticity. Further, although there
were significantly negative effects on career aspirations and
relationship agency resulting from a lack of relationship authenticity,
there was no evidence that this is due to feelings of sexual
objectification. The significant partner effect of objectification on
actor self-objectification suggests that women being objectified by
other women still results in feelings of self-objectification, and such
research has powerful implications for the ways that women interact in
both sexual and non-sexual settings.
}

@@

\section{Introduction}\label{introduction}

Theorists across diverse disciplines have explored the multiple ways
that the body conveys social meaning, as well as how these meanings
shape gendered experiences and therefore inform individuals' thinking,
feeling, and behavior, especially during interpersonal interactions with
members of different social groups (``Engendered lives,'' 1993).
Empirical evidence illustrates how women, in particular, continue to be
objects of perpetual discrimination as a result of psychosocial markers,
like gender, that produce modes through which their identity is
understood (Swim, Hyers, Cohen, \& Ferguson, 2001). Objectification
theory, a valuable theoretical framework proposed by Roberts and
Fredrickson (1997) which works to contextualize female bodies as
socio-cultural constructions, can be employed to illuminate the gender
oppression and negative lived experiences of girls and women.
Additionally, one of the most detrimental forms of discrimination
against them is thought to be the process by which their whole being is
viewed as a collection of sexualized body parts valued predominantly for
commodification, a phenomena termed sexual objectification (Bartky,
1990). Sexual objectification occurs with both \enquote{endless variety
and monotonous similarity,} and is thus mediated by unique combinations
of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
Nicholson (1989), p.~28). Amid such heterogeneity though,
\enquote{having a reproductively mature female body} proposed by Roberts
and Fredrickson (1997) is likely to create a shared vulnerability to
sexual objectification and a variety of shared negative experiences as a
result. Studies have shown that within social encounters women are gazed
at more than men (Briton \& Hall, 1995), often times feel
\enquote{looked at} within interpersonal interactions (Argyle \&
Williams, 1969), and will more than likely internalize the objectifying
gaze on physical self (Young, 1979). Moreover, perhaps the most adverse
effect of objectifying treatment is that it effectively socializes girls
and women to treat themselves as objects to be looked at and evaluated,
an effect termed self-objectification (Bartky, 1990; Berger, Cohen, \&
Zelditch Jr, 1972; L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge,
1998). Self-objectification is a multidimensional process that accounts
for the cognitive mechanism that translates experiences of sexualization
at the cultural level to psychological (e.g., anxiety, self-esteem,
authenticity, motivational states) and behavioral (cognitive
performance, body monitoring) features of mental health and well-being
at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011;
Moradi \& Huang, 2008). Calogero et al. (2011) proposes that the
construct of self-objectification can be conceptualized as a learned
trait. Furthermore, it can also be elicited momentarily, through the
media, for example, with sexualized images in movies and magazines,
which can lead to a state of self-objectification (Calogero et al.,
2011, Moradi and Huang (2008)). Being objectified by another person and
possessing trait-level self-objectification (TSO) may interact to
influence experiences of feeling like a body, or state
self-objectification (SSO). In the current work, we sought to examine
what occurs during an interaction in which one or both partners are
objectifying each other, similarly to Garcia, Earnshaw, and Quinn
(2016), but between same-sex female interpersonal interactions. We
predicted that being objectified by one's interaction partner would lead
to self-objectification, in addition to modified feelings of
authenticity in postinteraciton outcomes, including feelings of agency
in romantic relationships, career aspiration, and cognitive performance
(D. M. Quinn, Chaudoir, \& Kallen, 2011). Empirical evidence reveals
that objectification manifests through inauthenticity in romantic
relationships (Brunell et al., 2010), adverse attitudes in regard to
career aspirations, and a decrease in concentration and impairment in
female cognitive performance (Swim et al., 2001). Moreover, it was the
goal of this research to empirically explore the role of interaction
authenticity in objectification by utilizing a structural equation
modeling to examine the effects for both women simultaneously. We
expected to replicate the results found in the previous Garcia et al.
(2016) study. More specifically, we expected to find a positive
relationship between state-other objectification and self-state
objectification, and a resulting negative relationship between
self-state objectification and interaction authenticity. Finally, we
expected there to be a positive relationship between interaction
authenticity and cognitive performance, relationship agency, and career
aspirations.

@@

Data from two different samples were used for this study and are
discussed below. In the measures section that follows we refer to them
as Sample 1 and Sample 2. Sample 1 is from a co-ed liberal arts college
in the northeast and Sample 2 is from a women's liberal arts college in
the northeast.

@@

We used R (Version 3.4.1; R Core Team, 2017) and the R-packages
\emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
(Version 2.0.1; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
0.8.0.1; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.6; D. Kaplan
\& Pruim, 2017), \emph{ggplot2} (Version 3.1.0.9000; Wickham, 2016),
\emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
(Version 0.84; Gamer, Lemon, \&
\textless{}puspendra.pusp22@gmail.com\textgreater{}, 2012), \emph{knitr}
(Version 1.22; Xie, 2015), \emph{kutils} (Version 1.67; Johnson, Kite,
\& Redmon, 2019), \emph{lattice} (Version 0.20.35; Sarkar, 2008),
\emph{lavaan} (Version 0.6.3; Rosseel, 2012), \emph{lpSolve} (Version
5.6.13; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.10; Bates
\& Maechler, 2017), \emph{mosaic} (Version 1.1.0; Pruim, Kaplan, \&
Horton, 2017, 2016), \emph{mosaicData} (Version 0.14.0; Pruim et al.,
2016), \emph{nlme} (Version 3.1.131; Pinheiro, Bates, DebRoy, Sarkar, \&
R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
2018), \emph{psych} (Version 1.7.8; Revelle, 2017), \emph{purrr}
(Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
Wickham, 2019), \emph{tibble} (Version 2.1.1; Müller \& Wickham, 2019),
\emph{tidyr} (Version 0.8.3; Wickham \& Henry, 2019), \emph{tidyverse}
(Version 1.2.1; Wickham, 2017), \emph{usethis} (Version 1.4.0; Wickham
\& Bryan, 2018), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen,
Magnusson, \& Swinton, 2019) for all our analyses.

@@

This study sought to replicate the results of Garcia et al. (2016)'s
study, done with male-female pairs, which used dyadic analysis to detect
whether partners' objectification of one another affected state
self-objectification (SSO). See Figure~\ref{fig:2016figure} for the path
analysis results of the previous study. We hope to investigate how the
main effects found in the previous study relay to interactions between
women: specifically, the relationship between state-other
objectification and self-state objectification and the resulting effect
of self-state objectification on inauthenticity during the interaction.

We used path analysis to obtain our estimates, but because our sample is
nonindependent, we used the indistinguishable actor--partner
interdependence model (Olsen \& Kenny, 2006). The APIM can be defined as
a \enquote{model of dyadic relationships that integrates a conceptual
view of interdependence with the appropriate statistical techniques for
measuring and testing it} (Olsen \& Kenny, 2006). See
Figure~\ref{fig:apim} for a basic APIM model. Unlike the original Garcia
et al. (2016) study, our study deals with indistinguishable dyads,
meaning the designation of who is designated as \enquote{actor} and who
is designated as \enquote{partner} is arbitrary. Due to constraints of
the basic APIM, in that this was an exploration of indistinguishable
female dyads, we had to fix all path estimates to be the same
across/between people and partners, in addition to all variances,
covariances, endogenous intercepts, and exogenous means. Due to the
complexity of the original Garcia et al. (2016) study, we also had to
set the exogenous covariances equal. More specifically, the covariances
between TSO, actor and partner objectification, and the interaction
between actor TSO and partner objectification (and vice versa).

In order to interpret model fit, which refers to the ability of a model
to reproduce the data (i.e., usually the varience-covariance matrix) we
utilized both the I-SAT (saturated) model, and the Null model to ensure
that all possible corresponding covariences are fixed to be equal across
partners. We obtained fit estimates by subtracting the chi-square
estimate for the I-SAT model from the analysis model (Olsen \& Kenny,
2006, Peugh, DiLillo, and Panuzio (2013)).

@@

All model estimates and p-values are found in Table~\ref{tab:sem}. The
most important findings from Garcia et al. (2016) were the significant
partner effect between actor SSO and partner objectification
(specifically men's objectification of women and women's SSO), and the
link between actor SSO and actor authenticity (also specifically for
women). We did not find a significant effect between actor SSO and actor
authenticity (\(\beta\)= -.10, \(p\)=.38), which means we do not have
evidence to support the idea that partner objectification is the cause
for the negative effects related to relationship inauthenticity.
However, we did find a significant relationship between partner
objectification and actor SSO (\(\beta\)= .25, \(p\)=.03), which
supports our hypothesis that objectification from other women also
causes women to self-objectify just as it does in interactions between
male-female pairs. We also found a significantly negative effect of
authenticity on career aspirations (\(\beta\)= .18, \(p\)=.01) and
relationship agency (\(\beta\)=.27, \(p\)=.01). We found that the model
had good fit (\(\chi^2\)=22.33, \(df\)=34). In this case, a good fit
indicates that there are no direct effects of SSO or SOO on the outcomes
on cognitive performance, relationship agency, and career aspirations,
which indicates that the path we chose makes sense.

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:sem}Estimates from final Path Analysis Model}
\small{
\begin{tabular}{lllllll}
\toprule
Path & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{z-value} & \multicolumn{1}{c}{p-value}\\
\midrule
Actor SSO & \textasciitilde{} & Actor TSO & 0.08 & 0.09 & 0.91 & 0.36\\
Actor SSO & \textasciitilde{} & Actor Obj. of Partner & -0.17 & 0.12 & -1.41 & 0.16\\
Actor SSO & \textasciitilde{} & Partner Obj. of Actor & 0.25 & 0.12 & 2.15 & 0.03\\
Actor SSO & \textasciitilde{} & Actor TSO x Partner Obj. & 0.00 & 0.04 & -0.10 & 0.92\\
Actor Authenticity & \textasciitilde{} & Actor SSO & -0.10 & 0.12 & -0.88 & 0.38\\
Actor Cog. Performance & \textasciitilde{} & Actor Authenticity & 0.33 & 0.27 & 1.22 & 0.22\\
Actor Career Aspirations & \textasciitilde{} & Actor Authenticity & 0.18 & 0.07 & 2.66 & 0.01\\
Actor Rel. Agency & \textasciitilde{} & Actor Authenticity & 0.27 & 0.10 & 2.64 & 0.01\\
\bottomrule
\end{tabular}
}
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{verbatim}
## [1] "R [Version 3.4.1; @R-base]"
\end{verbatim}

@@

@@

@@

\hypertarget{ref-peugh2013analyzing}{}
Peugh, J. L., DiLillo, D., \& Panuzio, J. (2013). Analyzing mixed-dyadic
data using structural equation models. \emph{Structural Equation
Modeling: A Multidisciplinary Journal}, \emph{20}(2), 314--337.

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, \& Asha Hinson},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Objectification in Action: Self- and Other-Objectification in
Same-gender Interactions}
    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
Kyuchukova\textsuperscript{1}, \& Asha Hinson\textsuperscript{1}}
    \date{}

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{

Correspondence concerning this article should be addressed to Randi L.
Garcia, 415 Bass Hall, Smith College, Northampton, MA 01060. E-mail:
\href{mailto:rgarcia@smith.edu}{\nolinkurl{rgarcia@smith.edu}}}

\abstract{
Empirical evidence has only found links between objectification,
self-objectification, and negative outcomes for woman within
interpersonal interactions between male-female pairs. The purpose of the
present study was to extend past research and consider the relationships
between such valuable phenomena and their effects on authenticity within
interactions between female pairs. Woman were brought into the
laboratory and interacted in same-sex dyads. Dyadic analysis was
utilized to detect whether partners' objectification of each other
affected state self-objectification, and the resulting feelings of
comfort and authenticity during the interaction. After the interaction,
participants completed a questionnaire which measured many constructs
including cognitive performance, career aspirations, and relationship
agency. Results revealed no significant relationship between
self-objectification and authenticity. Further, although there were
significantly negative effects on career aspirations and relationship
agency resulting from a lack of relationship authenticity, there was no
evidence that this is due to feelings of sexual objectification. The
significant partner effect of objectification on actor
self-objectification suggests that women being objectified by other
women still results in feelings of self-objectification, and such
research has powerful implications for the ways that women interact in
both sexual and non-sexual settings. AUTHOR NOTE: mention Clark trigram
coders Hannah et al.

}

@@

Theorists across diverse disciplines have explored the multiple ways
that the body conveys social meaning, as well as how these meanings
shape gendered experiences, especially during interpersonal interactions
with members of different social groups (``Engendered lives,'' 1993,
Garcia, Earnshaw, and Quinn (2016)). Objectification theory, a valuable
theoretical framework proposed by Roberts and Fredrickson (1997) which
works to contextualize female bodies as socio-cultural constructions,
can be employed to illuminate the gender oppression and negative lived
experiences of girls and women. Empirical evidence illustrates how women
continue to be objects of interpersonal discrimination and expereince
daily sexist hassles (Swim, Hyers, Cohen, \& Ferguson, 2001). One form
of interpersonal discrimination women face is the process by which their
whole being is viewed as a collection of sexualized body parts valued
predominantly for commodification, a phenomena termed sexual
objectification (Bartky, 1990). Sexual objectification occurs with both
\enquote{endless variety and monotonous similarity,} and is thus
mediated by unique combinations of race, ethnicity, sexuality, age, and
class (Fredrickson, Hendler, Nilsen, O'Barr, \& Roberts, 2011; Rubin,
1975, cited in Fraser and Nicholson (1989), p.~28). Amid such
heterogeneity though, \enquote{having a reproductively mature female
body} proposed by Roberts and Fredrickson (1997) is likely to create a
shared vulnerability to sexual objectification and a variety of shared
negative experiences as a result.

Self-objectification is a multidimensional process that accounts for the
cognitive mechanism that translates experiences of sexualization at the
cultural level to psychological (e.g., anxiety, self-esteem,
authenticity, motivational states) and behavioral (cognitive
performance, body monitoring) features of mental health and well-being
at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011;
Moradi \& Huang, 2008). Calogero et al. (2011) proposes that the
construct of self-objectification can be conceptualized as a learned
trait. Furthermore, it can also be elicited momentarily, through the
media, for example, with sexualized images in movies and magazines,
which can lead to a state of self-objectification (Calogero et al.,
2011, Moradi and Huang (2008)). Being objectified by another person and
possessing trait-level self-objectification (TSO) may interact to
influence experiences of feeling like a body, or state
self-objectification (SSO) (CITE swimsuit sweater, Garcia et al., 2016).

Studies have shown that within social encounters women are gazed at more
than men (Briton \& Hall, 1995, CITE saguy skype study, calogero video
walking study), often times feel \enquote{looked at} within
interpersonal interactions (Argyle \& Williams, 1969), and will more
than likely internalize the objectifying gaze on physical self (Young,
1979). Moreover, perhaps the most adverse effect of objectifying
treatment is that it effectively socializes girls and women to treat
themselves as objects to be looked at and evaluated, an effect termed
self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972;
L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge, 1998).

ENTIRE PARAGRAPH ON MODERN (POST-2016) STUDIES OF INTERPERSONAL
OBJECTIFICATION.

Empirical evidence reveals that objectification manifests through
inauthenticity in romantic relationships (Brunell et al., 2010), adverse
attitudes in regard to career aspirations, and a decrease in
concentration and impairment in female cognitive performance (D. M.
Quinn, Chaudoir, \& Kallen, 2011).

In the current study, we sought to examine what occurs during an
interaction in which one or both partners are objectifying each other,
similarly to Garcia et al. (2016), but between same-sex female
interpersonal interactions. Moreover, the current study uses a
face-to-face interaction paradigm and dyadic data analysis techniques to
examine the effects for both women simultaneously. We expected to
replicate the results found in Garcia et al. (2016). We predicted that
being objectified by one's interaction partner would lead to
self-objectification, which in turn would lead to feelings of
inauthenticity, then reduced feelings of agency in romantic
relationships, reduced career aspiration, and reduced cognitive
performance. Specifically, we expected to find a positive relationship
between other-objectification by one's partner and state
self-objectification. We also expect to find a negative relationship
between self-state objectification and interaction authenticity, and
that interaction authenticity will be positively related to cognitive
performance, relationship agency, and career aspirations.

@@

Data from two different, but demographically equivalent, samples were
combined to create the final analysis sample (\emph{N =} 64) used in
this study. In the measures section that follows we refer to them as
Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
women's liberal arts college in the northeast US.

@@

We used R (Version 3.5.2; R Core Team, 2017) and the R-packages
\emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools}
(Version 1.13.5; Wickham, Hester, \& Chang, 2018), \emph{dplyr} (Version
0.8.3; Wickham, François, Henry, \& Müller, 2018), \emph{forcats}
(Version 0.3.0; Wickham, 2018), \emph{ggformula} (Version 0.7.0; D.
Kaplan \& Pruim, 2017), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
\emph{haven} (Version 2.1.0; Wickham \& Miller, 2019), \emph{irr}
(Version 0.84.1; Gamer, Lemon, \&
\textless{}puspendra.pusp22@gmail.com\textgreater{}, 2012), \emph{knitr}
(Version 1.25; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite,
\& Redmon, 2019), \emph{lattice} (Version 0.20.38; Sarkar, 2008),
\emph{lavaan} (Version 0.6.1; Rosseel, 2012), \emph{lpSolve} (Version
5.6.15; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.15; Bates
\& Maechler, 2017), \emph{mosaic} (Version 1.2.0; Pruim, Kaplan, \&
Horton, 2017, 2016), \emph{mosaicData} (Version 0.17.0; Pruim et al.,
2016), \emph{nlme} (Version 3.1.137; Pinheiro, Bates, DebRoy, Sarkar, \&
R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth,
2018), \emph{psych} (Version 1.8.4; Revelle, 2017), \emph{purrr}
(Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.1.1;
Wickham, Hester, \& Francois, 2017), \emph{stringr} (Version 1.4.0;
Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse}
(Version 1.2.1; Wickham, 2017), \emph{usethis} (Wickham \& Bryan, 2018),
and \emph{xtable} (Version 1.8.3; Dahl, Scott, Roosen, Magnusson, \&
Swinton, 2019) for all our analyses.

@@

This study sought to replicate the results of Garcia et al. (2016)'s
study, done with male-female pairs, which used a dyadic path analysis to
detect whether partners' objectification of one another affected state
self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
results of the analysis from this previous study. We hope to investigate
how the central effects found in the previous study relate to
interactions between two women. Specifically, we are interested in
testing the relationship between state-other objectification and SSO,
and how SSO in turn, affecs feelings of inauthenticity during the
interaction. In addition, we will also test if the effect of
other-objectification in an interaction on SSO is only present for those
women who are high in trait self-objectification, as in Garcia et al.
(2016). Further, we will investigate the realtionships between
experiencing interaction inauthenticity and relationship agency, career
aspirations, and cognitive performance.

While Garcia et al. (2016) used dyadic path analysis, we will conduct
our dyadic analyses using multilevel modeling. Dyadic analyses for
distingishable dyads (e.g., mixed-gender interacting pairs) is more
natural in Structual Equation Modeling (SEM) than it is for
indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
this asymmetry is that, due to the arbitrary distinctions made bewteen
\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
many estimates need to be fixed to be equal (i.e., paths, variances,
covariances, endogenous intercepts, and exogenous means) for
indistinguishable dyads but these equality contraints should not then be
considered in the degrees of freedom calculations for fit estimations
(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
independence model and the corresponding fit measure should be
re-calculated for indistinguishable dyads models. The current study uses
dyadic multilevel modeling (MLM) to test all relationships and mediation
paterns. See Ledermann and Kenny (2017) for a more complete discussion
of the considerations for using SEM versus MLM for dyadic analysis.

Testing the Garcia et al. (2016) model on the current, same-gender,
sample, involves using the Actor-Partner Independence Model (APIM)
approch for each outcome variable (i.e., endogenous variable in
Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
model. The APIM includes effects due to one's own, as well as one's
partner's, predictor variables (\(X\)'s) on the one's own outcome
variable (\(Y\)). Unlike the original Garcia et al. (2016) study, our
study deals with indistinguishable dyads, meaning the designation of who
is designated as \enquote{actor} and who is designated as
\enquote{partner} is arbitrary. Recall that the indistinguiahble nature
of the dyads in the current study led us to choose the MLM approach over
SEM. These analyses are considered exploratory, given the lack of prior
research theorizing about these linkages.

@@

All model estimates and p-values are found in Table~\ref{tab:mlm} and
the relationships with estimates included are depicted in
Figure~\ref{fig:semfigure}.

The most important finding from Garcia et al. (2016) was the significant
partner effect of other objectification and SSO (specifically men's
objectification of women and women's SSO). As expected, the partner
effect of other-objectification on SSO in the current all-women sample
was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
\emph{p} = .017, replicating Garcia et al. (2016)'s fiding. One's own
other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
= 0.12, \emph{p} = .193. Contrary to past finding however, there was no
statistically significant interaction of partner's other objectification
and the person's trait self-objectification on SSO, \emph{b} = -0.02,
\emph{SE} = 0.04, \emph{p} = .589. There was also no significant main
effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
0.05, \emph{p} = .170.

Contrary to expectations, there was no significant effect of SSO on
interaction authenticity, although the estimate of this effect was in
the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.11,
\emph{p} = .415. Because authenticity was a composite score of 9 items,
two of which were interaction specific authenticity items, we also
tested the effect of SSO on these items individually\ldots{}ADD
ANALYSIS\ldots{}Although we hypothesized that SSO would mediate the
relationship between partner's other objectification and interaction
authenticity, after finding no relationship bewteen SSO and authencity,
we also tested if the partner's other objectification had a direct
effect on authenticity, but this effect was not significant, \emph{b} =
0.05, \emph{SE} = 0.11, \emph{p} = .662 (nor was the total effect of
partner's other objectification on authenticity, \emph{b} = 0.02,
\emph{SE} = 0.1, \emph{p} = .855).

Lastly, althought there was no evidence that SSO was related to
interaction authenticity in the current sample, we tested if interaction
authenticity (composite of nine items) had effects on cognitive
performace, career aspirations, and relationship agency, as it did in
Garcia et al. (2016). We again used MLM and thus, these efefcts were
tested in three separate models. There was no significant effect of
interaction authenticity on cognitive performance, \emph{b} = 0.31,
\emph{SE} = 0.28, \emph{p} = .262, but authenticity was significantly
positively related to both career aspirations, \emph{b} = 0.19,
\emph{SE} = 0.07, \emph{p} = .009, and relationships agency, \emph{b} =
0.23, \emph{SE} = 0.12, \emph{p} = .048. There was no direct effect of
SSO on cognitive performance, \emph{b} = 0.05, \emph{SE} = 0.25,
\emph{p} = .846, and no direct effect of partner's other objectificaiton
on cognifitve performance, \emph{b} = 0.03, \emph{SE} = 0.26, \emph{p} =
.900. There was no direct effect of SSO on career aspirations, \emph{b}
= 0.03, \emph{SE} = 0.06, \emph{p} = .653, and no direct effect of
partner's other objectificaiton on career aspirations, \emph{b} = -0.05,
\emph{SE} = 0.06, \emph{p} = .405. There was no direct effect of SSO on
relationship agency, \emph{b} = -0.04, \emph{SE} = 0.11, \emph{p} =
.699, and no direct effect of partner's other objectificaiton on
relationship agency, \emph{b} = -0.07, \emph{SE} = 0.1, \emph{p} = .474.

@@

@@

@@

\hypertarget{ref-garcia2015moderation}{}
Garcia, R. L., Kenny, D. A., \& Ledermann, T. (2015). Moderation in the
actor--partner interdependence model. \emph{Personal Relationships},
\emph{22}(1), 8--29.

@@

\hypertarget{ref-ledermann2017analyzing}{}
Ledermann, T., \& Kenny, D. A. (2017). Analyzing dyadic data with
multilevel modeling versus structural equation modeling: A tale of two
methods. \emph{Journal of Family Psychology}, \emph{31}(4), 442.

@@
